Experiment 2

### 2018-03-15 experiment_2/experiment_2.tex
updated experiment 2

Comments: The story I seem to get from this is (roughly) that the worse the algorithm that the incumbent plays is, the better the entrant will do. However, in order for the entrant to do as well as possible, the entrant should play a worse algorithm! This seems counterintuitive, it means that the worst case for the entrant is when we're both playing ThompsonSampling and the best case for the entrant is when we're both playing DynamicGreedy.

>>>>

Comments: The story I seem to get from this is (roughly) that the worse the algorithm that the incumbent plays is, the better the entrant will do. Thus, the incumbent should want to play a better algorithm. However, in order for the entrant to do as well as possible, the entrant should in fact play a worse algorithm! This is interesting but I'm not sure it is intuitive.
